Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2020-07-01 paper/ifo-complexAudio.tex
Butterworth plots

\begin{figure}
	\includegraphics[width=.49\textwidth]{figures/podo_noise_psd_zoom-cropped.pdf}
	\caption{\label{fig:psd_noise}
Power spectral density (PSD) of the optical microphone  with no injected audio (i.e.\ with the speaker off). 
We see strong power from the $50\,{\rm Hz}$ mains hum and its harmonics (most likely from the photodiode circuit and the room’s lighting and cooling). 
Otherwise the PSD is fairly white. 
}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.49\textwidth]{figures/butterworth_150_3000-cropped.pdf}
	\caption{Butterworth bandpass filter frequency response, any amplitude beyond $-3\,{\rm dB}$ is significant attenuation (half power). The green vertical lines show the band limits of $150\,{\rm Hz}$ and $3\,{\rm kHz}$. Note the flat response within the band.
	\jam{[to do: change green lines to dashed and red. add panel with PSD after applying Butterworth bandpass]}}
	\label{fig:butterworth}
\end{figure}

>>>>

\begin{figure}
	\includegraphics[width=.49\textwidth]{figures/psd_butterworth_14_6.pdf}
	\caption{\label{fig:psd_noise}
Power spectral density (PSD) of background noise (top) from the optical microphone (with the speaker off), and the PSD after applying a Butterworth bandpass filter (bottom) between the two frequencies marked with red, dashed lines. 
We see strong power from the $50\,{\rm Hz}$ mains hum and its harmonics (most likely from the photodiode circuit and the room’s lighting and cooling). Otherwise the PSD is fairly white. 
After filtering we see strong attenuation of all frequencies outside the band, but little change to the harmonics within the band.
}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.49\textwidth]{figures/butterworth_150_3000.pdf}
	\caption{Butterworth bandpass filter frequency response, any amplitude beyond $-3\,{\rm dB}$ is significant attenuation (half power). The red, dashed vertical lines show the band limits of $150\,{\rm Hz}$ and $3\,{\rm kHz}$. Note the flat response within the band.}
	\label{fig:butterworth}
\end{figure}
